\LARGE \bf Enhancing Security in Multi-Robot Systems through Co-Observation Planning, Reachability Analysis, and Network Flow

### 2024-11-12 paper.tex
update

A preliminary version of the paper was presented in \cite{yang2020multi,yang2021multi}. Extanding the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in the ADMM-based trajectory optimization solver to accomodate for more flexible objectives. In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature. This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. Inspired by the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the context of the $\mathtt{RRT^*}$ path planning algorithm, we utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.

@@

Graph-based search is another extensively explored approach in trajectory planning problems, such as formation control \cite{tanner2004leader,hu2019distributed} and Multi-Agent Path Finding (MAPF) problems \cite{stern2019multi}. In traditional MAPF formulations, environments are abstracted as graphs, with nodes representing positions and edges denoting possible transitions between positions and solved as a network flow problem \cite{yu2013multi,yu2016optimal}. This formulation allows for the application of combinatorial network flow algorithms and linear program techniques, offering efficient and more flexible solutions to the planning problem. %In contrast with such approach, our research in \Cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
\rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}

In \Cref{sec:ADMM-planning}, we incorporate reachability constraints to increase overall security Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. One typical approach involves computing an over-approximation of the reachable space for checking safety properities. Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric representation, such as zonotopes and ellipsoids, as a compact enclosure of the reachability sets. In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions.

@@

@@

%This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories.

\rtron{Clarify when we use bold symbols. Make sure this is used consistently.}
We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space. For a total of $n_p$ robots, and a task time horizon of $T$, a total of $n_p$ trajectories can be represented as an aggregated vector $\vq\in \real{n m T}$. 
The overall goal is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis). Formally:
\begin{equation}\label{eq:general-problem}
	\begin{split}
		\min/\max & \quad \varPhi(\vq)\\
		\textrm{subject to} &\quad \vq \in \Omega.
	\end{split}
\end{equation}

@@

{\small
\bibliographystyle{unsrt}
\bibliography{ADMM_planning,ACC,tron,ziqi,reachability}
}

>>>>

A preliminary version of the paper was presented in \cite{yang2020multi,yang2021multi}. Extanding the grid-world solution from \cite{wardega2019resilience} to continuous configuration spaces, we incorporate the co-observation planning as constraints in the ADMM-based trajectory optimization solver to accomodate for more flexible objectives. In this paper, we incorporate additional reachability analysis during the planning phase, incorporating constraints based on sets of locations that agents could potentially reach, referred to as \emph{reachability regions}, as a novel perspective to the existing literature. This approach enforces an empty intersection between forbidden regions and the reachability region during trajectory optimization, preventing undetected attacks if an adversary gains control of the robots. We utilize an ellipsoidal boundary to constrain the search space and formulate the ellipsoid as the reachability region constraint. We present a mathematical formulation of reachability regions compatible with the solver in \cite{yang2020multi} as a spatio-temporal constraint.

@@

Graph-based search is another extensively explored approach in trajectory planning problems, such as formation control \cite{tanner2004leader,hu2019distributed} and Multi-Agent Path Finding (MAPF) problems \cite{stern2019multi}. In traditional MAPF formulations, environments are abstracted as graphs, with nodes representing positions and edges denoting possible transitions between positions and solved as a network flow problem \cite{yu2013multi,yu2016optimal}. This formulation allows for the application of combinatorial network flow algorithms and linear program techniques, offering efficient and more flexible solutions to the planning problem. %In contrast with such approach, our research in \Cref{sec:cross-trajectory} abstracts the existing Multi-Robot System (MRS) trajectory (instead of the environment) into a directed graph and formulates the cross-trajectory co-observation paths as flows.
% \rtron{Cite the paper from the reviewer, as well as the paper from Tedrake on the IRIS decomposition, saying that ellipsoids have been used to create approximations of the free configuration space, not to bound reacheability, and not for security application here.}

Reachability analysis is a important step in the security and safety verification synthesis for cyber-physical systems (CPSs) \cite{gueguen2009safety,ding2020secure}. One typical approach involves computing an over-approximation of the reachable space for checking safety properities. Previous studies \cite{kurzhanski2000ellipsoidal,lakhal2019interval,maiga2015comprehensive} often use geometric representation, such as zonotopes and ellipsoids, as a compact enclosure of the reachability sets. In the realm of online safety assessment against cyber attacks, \cite{kwon2017reachability} computed the reachable set of CPS states achievable by potential cyber attacks and compared it with the safe region, set based on current state estimation and environmental conditions. With the incorporation of an additional security measure that provides two known states instead of one, we can simplify the reachable region using an ellipsoidal over-approximation. The use of ellipsoids is well-established in path planning methods due to their smooth, continuous boundaries and defined geometric properties, which enable efficient optimization. Notable examples include Iterative Regional Inflation by Semidefinite programming (IRIS) \cite{deits2015computing, ray2022free} and the Safe Flight Corridor (SFC) \cite{liu2017planning, fan2024flying}. Both IRIS and SFC utilize ellipsoids to approximate the free configuration space; however, these methods are designed to plan specific, safe paths with dynamics in mind, rather than mapping all possible outcomes. This focus limits their applicability in security contexts. Our work is inspired by another ellipsoidal application, the \emph{heuristic sampling domain} introduced by \cite{gammell2014informed} within the framework of the $\mathtt{RRT^*}$ path planning algorithm.

@@

\noindent\myparagraph{Notation} 
In this paper, we use non-bold symbols like to denote single-agent states (i.e. $q_{ij}$), while bold symbols represent aggregated states involving multiple agents (i.e. $\vq$). \zyang{does regular scalers need mention?}

@@

%This problem is first solved by \cite{wardega2019resilience} in grid world for robots with fixed start and goal locations (Figure~\ref{fig:Grid-example-application}) but does not offer the ability to optimize arbitrary smooth cost functions of the trajectories. 
We formulate the planning problem as an optimal trajectory optimization problem to minimize arbitrary smooth objective functions. We denote as $q_{ij}\in\real{m}$ the position of agent $i$ at the discrete-time index $j$, with $m$ representing the dimension of the state space. For a total of $n_p$ robots, and a task time horizon of $T$, a total of $n_p$ trajectories can be represented as an aggregated vector $\vq\in \real{n m T}$. 
The overall goal is to minimize or maximize an objective function $\varPhi(\vq)$ under a set of nonlinear constraints described by a set $\Omega$, which is given by the intersection of spatio-temporal sets given by traditional path planning constraintsand the security constraints (co-observation schedule, reachability analysis). Formally:
\begin{equation}\label{eq:general-problem}
	\begin{split}
		\min/\max & \quad \varPhi(\vq)\\
		\textrm{subject to} &\quad \vq \in \Omega.
	\end{split}
\end{equation}

@@

{\small
\bibliographystyle{IEEEtran}
\bibliography{ADMM_planning,ACC,tron,ziqi,reachability}
}
